---
title: "testresults20250121"
author: "Zoe Mozola"
date: "2025-01-21"
output: html_document
---

``` {r Setup}

library(tidyverse)
library(here)
library(janitor)
library(ggplot2)
library(ggsignif)
library(ggpubr)

filepath <- "C:/Users/zoemo/OneDrive/Desktop/Hendry Lab"


```

```{r Read-In}
data1 <- read_csv("C:/Users/zoemo/OneDrive/Desktop/Hendry Lab/ZM Data Sheet - Copy.csv")
data2 <- read_csv("C:/Users/zoemo/OneDrive/Desktop/Hendry Lab/ZM Data Sheet 250127.csv")
data3 <- read_csv("C:/Users/zoemo/OneDrive/Desktop/Hendry Lab/ZM Data Sheet With Other.csv")
data4 <- read_csv("C:/Users/zoemo/OneDrive/Desktop/Hendry Lab/ZM Data Sheet Cleaned.csv")
data5 <- read_csv("C:/Users/zoemo/OneDrive/Desktop/Hendry Lab/ZM Data Sheet Cleaned Reduced.csv")


```

```{r Cleaning}
# Set Current dataset 
data <- data5


#Encleanenate
dataclean <- data %>%
  clean_names() %>%
  filter(!is.na(fish_id)) %>%
  #Make that shit categorical
  mutate(time_period = ifelse(year >= 2000, "Present", "Historical")) %>%
  #Make tag for unarmoured/giant
  mutate(type = ifelse(body_of_water %in% c("Drizzle Lake", "Mayer Lake"), "Giant", "Unarmoured")) %>%
  #Make Plate Arrangement a string
  mutate(plate_l_combined = as.factor(plate_l_combined)) %>%
  mutate(plate_r_combined = as.factor(plate_r_combined)) %>%
  mutate(body_of_water = factor(body_of_water, levels = c("Mayer Lake", "Drizzle Lake",
                                            "Serendipity Lake", "Boulton Lake", 
                                            "Rouge Lake")))

#ALLOMETRIC ADJUSTMENTS
data.log <- dataclean %>%
  mutate_at(vars(sl, body_depth, ap_length_corrected, ap_width_corrected, jaw_length, ppl, ppw, dorsal_1, dorsal_2, pelvic_spine, eye_diameter),
                  log10)

# size.coef is a function to get coefficient for #size adjustment #trait - name of trait col to get #slope coefficient
size.coef<-function(trait){
  ancova=lm(data=data.log, trait~sl+body_of_water)
  coef=ancova$coefficients[2]
  coef
}

#the following line produces slope coefficient. #Repeat for each trait.
BD.coef<-size.coef(data.log$body_depth)
APL.coef<-size.coef(data.log$ap_length_corrected)
APW.coef<-size.coef(data.log$ap_width_corrected)
JL.coef<-size.coef(data.log$jaw_length)
PPL.coef<-size.coef(data.log$ppl)
PPW.coef<-size.coef(data.log$ppw)
D1.coef<-size.coef(data.log$dorsal_1) #log of 0 is infinity
D2.coef<-size.coef(data.log$dorsal_2)
PS.coef<-size.coef(data.log$pelvic_spine)
ED.coef<-size.coef(data.log$eye_diameter)

# following makes a matrix 1 x k matrix of slopes for each trait
Coef<-matrix(c(BD.coef, APL.coef, APW.coef,JL.coef, PPL.coef, PPW.coef, D1.coef, D2.coef, PS.coef, ED.coef),dimnames = list(c("body_depth", "ap_length", "ap_width", "jaw_length", "ppl", "ppw", "dorsal_1", "dorsal_2", "pelvic", "eye")))


# Adjusts trait value using formula: Xadj=Xi*(mean(sl)/SLi)^b
dataclean$body_depth.adj<-dataclean$body_depth*(mean(dataclean$sl)/dataclean$sl)^Coef["body_depth",]
dataclean$ap_length.adj<-dataclean$ap_length_corrected*(mean(dataclean$sl)/dataclean$sl)^Coef["ap_length",]
dataclean$ap_width.adj<-dataclean$ap_width_corrected*(mean(dataclean$sl)/dataclean$sl)^Coef["ap_width",]
dataclean$jaw_length.adj<-dataclean$jaw_length*(mean(dataclean$sl)/dataclean$sl)^Coef["jaw_length",]
dataclean$ppl.adj<-dataclean$ppl*(mean(dataclean$sl)/dataclean$sl)^Coef["ppl",]
dataclean$ppw.adj<-dataclean$ppw*(mean(dataclean$sl)/dataclean$sl)^Coef["ppw",]
dataclean$dorsal_1.adj<-dataclean$dorsal_1*(mean(dataclean$sl)/dataclean$sl)^Coef["dorsal_1",]
dataclean$dorsal_2.adj<-dataclean$dorsal_2*(mean(dataclean$sl)/dataclean$sl)^Coef["dorsal_2",]
dataclean$pelvic_spine.adj<-dataclean$pelvic_spine*(mean(dataclean$sl)/dataclean$sl)^Coef["pelvic",]
dataclean$eye_diameter.adj<-dataclean$eye_diameter*(mean(dataclean$sl)/dataclean$sl)^Coef["eye",]





#Make Boulton
boulton <- dataclean %>%
  filter(body_of_water=="Boulton Lake")
  

#Make Drizzle
drizzle <- dataclean %>%
  filter(body_of_water=="Drizzle Lake")

#Make Mayer
mayer <- dataclean %>%
  filter(body_of_water=="Mayer Lake")

#Make Serendipity
serendipity <- dataclean %>%
  filter(body_of_water=="Serendipity Lake")

#Make Rouge
rouge <- dataclean %>%
  filter(body_of_water=="Rouge Lake")



```


```{r Check for outliers unadjusted}

#All Lakes
ggplot(dataclean, aes(x = sl, y = body_depth)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ap_length_corrected)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ap_width_corrected)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = jaw_length)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ppl)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ppw)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = dorsal_1)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = dorsal_2)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = pelvic_spine)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = eye_diameter)) + geom_point() + geom_text(aes(label = fish_id))


#Boulton
ggplot(boulton, aes(x = sl, y = body_depth)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ap_length_corrected)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ap_width_corrected)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = jaw_length)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ppl)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ppw)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = dorsal_1)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = dorsal_2)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = pelvic_spine)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = eye_diameter)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")

#Mayer
ggplot(mayer, aes(x = sl, y = body_depth)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ap_length_corrected)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ap_width_corrected)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = jaw_length)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ppl)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ppw)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = dorsal_1)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = dorsal_2)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = pelvic_spine)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = eye_diameter)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")

#Drizzle
ggplot(drizzle, aes(x = sl, y = body_depth)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ap_length_corrected)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ap_width_corrected)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = jaw_length)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ppl)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ppw)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = dorsal_1)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = dorsal_2)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = pelvic_spine)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = eye_diameter)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")

#Serendipity
ggplot(serendipity, aes(x = sl, y = body_depth)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ap_length_corrected)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ap_width_corrected)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = jaw_length)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ppl)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ppw)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = dorsal_1)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = dorsal_2)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = pelvic_spine)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = eye_diameter)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")

#Rouge
ggplot(rouge, aes(x = sl, y = body_depth)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ap_length_corrected)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ap_width_corrected)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = jaw_length)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ppl)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ppw)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = dorsal_1)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = dorsal_2)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = pelvic_spine)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = eye_diameter)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")


```


```{r Check for outliers adjusted}
#All lakes together
ggplot(dataclean, aes(x = sl, y = body_depth.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ap_length.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ap_width.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = jaw_length.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ppl.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = ppw.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = dorsal_1.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = dorsal_2.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = pelvic_spine.adj)) + geom_point() + geom_text(aes(label = fish_id))
ggplot(dataclean, aes(x = sl, y = eye_diameter.adj)) + geom_point() + geom_text(aes(label = fish_id))

#Boulton
ggplot(boulton, aes(x = sl, y = body_depth.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ap_length.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ap_width.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = jaw_length.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ppl.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = ppw.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = dorsal_1.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = dorsal_2.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = pelvic_spine.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")
ggplot(boulton, aes(x = sl, y = eye_diameter.adj)) + geom_point(color = "purple") + geom_text(aes(label = fish_id), color = "purple")

#Mayer
ggplot(mayer, aes(x = sl, y = body_depth.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ap_length.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ap_width.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = jaw_length.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ppl.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = ppw.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = dorsal_1.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = dorsal_2.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = pelvic_spine.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")
ggplot(mayer, aes(x = sl, y = eye_diameter.adj)) + geom_point(color = "darkorange2") + geom_text(aes(label = fish_id), color = "darkorange2")

#Drizzle
ggplot(drizzle, aes(x = sl, y = body_depth.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ap_length.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ap_width.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = jaw_length.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ppl.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = ppw.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = dorsal_1.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = dorsal_2.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = pelvic_spine.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")
ggplot(drizzle, aes(x = sl, y = eye_diameter.adj)) + geom_point(color = "chartreuse4") + geom_text(aes(label = fish_id), color = "chartreuse4")

#Serendipity
ggplot(serendipity, aes(x = sl, y = body_depth.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ap_length.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ap_width.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = jaw_length.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ppl.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = ppw.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = dorsal_1.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = dorsal_2.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = pelvic_spine.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")
ggplot(serendipity, aes(x = sl, y = eye_diameter.adj)) + geom_point(color = "blue") + geom_text(aes(label = fish_id), color = "blue")

#Rouge
ggplot(rouge, aes(x = sl, y = body_depth.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ap_length.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ap_width.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = jaw_length.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ppl.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = ppw.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = dorsal_1.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = dorsal_2.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = pelvic_spine.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")
ggplot(rouge, aes(x = sl, y = eye_diameter.adj)) + geom_point(color = "red") + geom_text(aes(label = fish_id), color = "red")

```



2 way anova interaction of time and site with trait :/
```{r Preliminary stats undefined eval=FALSE, include=FALSE}

#Big Anovas

#Anova for SL 
#(time period NOT sig, water body SIG, SIG interaction as well)
slanova <- aov(sl ~ time_period + body_of_water + time_period:body_of_water, data = dataclean)
summary(slanova)

#Anova for plates total L 
#(time period SIG and water body SIG, interaction NOT sig, this means that time period has same effect throughout water bodies)
planova <- aov(plate_l_total ~ time_period + body_of_water + time_period:body_of_water, data = dataclean)
summary(planova)

#Anova for body depth
#(time period NOT sig, water body SIG, interaction SIG)
bdanova <- aov(body_depth ~ time_period + body_of_water + time_period:body_of_water, data = dataclean)
summary(bdanova)


# T Tests

#SL Boulton (sig increase)
t.test(sl ~ time_period, data = boulton)

#SL Drizzle
t.test(sl ~ time_period, data = drizzle)

#SL Mayer (sig increase)
t.test(sl ~ time_period, data = mayer)

#SL Serendipity
t.test(sl ~ time_period, data = serendipity)

#SL Rouge (sig decrease)
t.test(sl ~ time_period, data = rouge)




#Left Plates Boulton (Almost sig increase?)
t.test(plate_l_total ~ time_period, data = boulton)

#Left Plates Drizzle
t.test(plate_l_total ~ time_period, data = drizzle)

#Left Plates Mayer (SIG INCREASE)
t.test(plate_l_total ~ time_period, data = mayer)

#Left Plates Serendipity
t.test(plate_l_total ~ time_period, data = serendipity)

#Left Plates Rouge (SIG INCREASE)
t.test(plate_l_total ~ time_period, data = rouge)




#Body Depth Boulton (SIG INCREASE)
t.test(body_depth ~ time_period, data = boulton)

#Body Depth Drizzle
t.test(body_depth ~ time_period, data = drizzle)

#Body Depth Mayer
t.test(body_depth ~ time_period, data = mayer)

#Body Depth Serendipity
t.test(body_depth ~ time_period, data = serendipity)

#Body Depth Rouge
t.test(body_depth ~ time_period, data = rouge)

```


```{r Plotting Preliminary, eval=FALSE, include=FALSE}

#SL Boulton
ggplot(data = boulton, aes(x = time_period, y = sl)) +
  geom_boxplot() +
  labs(title = "Boulton Lake Standard Length Historical/Present", 
       x = "Time Period", y = "Standard Length (mm)") +
  theme_minimal()

#SL All
ggplot(data = dataclean, aes(x = time_period, y = sl, color = body_of_water)) +
  geom_boxplot() +
  labs(title = "All Lakes Standard Length Historical/Present", 
       x = "Time Period", y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Lake")

#SL All but grouped by lake
ggplot(data = dataclean, aes(x = body_of_water, y = sl, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Standard Length Historical/Present", 
       x = "Lake", y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")




#Body Depth Boulton
ggplot(data = boulton, aes(x = time_period, y = body_depth)) +
  geom_boxplot() +
  labs(title = "Boulton Lake Body Depth Historical/Present", 
       x = "Time Period", y = "Body Depth (mm)") +
  theme_minimal()

#Body Depth All
ggplot(data = dataclean, aes(x = time_period, y = body_depth, color = body_of_water)) +
  geom_boxplot() +
  labs(title = "All Lakes Body Depth Historical/Present", 
       x = "Time Period", y = "Body Depth (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Lake")

#Body Depth All but grouped by lake
ggplot(data = dataclean, aes(x = body_of_water, y = body_depth, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Body Depth Historical/Present", 
       x = "Lake", y = "Body Depth (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")





#Plate Total L Mayer
ggplot(data = mayer, aes(x = time_period, y = plate_l_total)) +
  geom_boxplot() +
  labs(title = "Mayer Total Left Lateral Plate Count Historical/Present", 
       x = "Time Period", y = "Number of Left Lateral Plates") +
  theme_minimal()

#Plate Total L All
ggplot(data = dataclean, aes(x = time_period, y = plate_l_total, color = body_of_water)) +
  geom_boxplot() +
  labs(title = "All Lakes Total Left Lateral Plate Count Historical/Present", 
       x = "Time Period", y = "Number of Left Lateral Plates") +
  theme_minimal() +
  scale_color_discrete(name = "Lake")

#Plate Total L All but grouped by lake
ggplot(data = dataclean, aes(x = body_of_water, y = plate_l_total, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Total Left Lateral Plate Count Historical/Present", 
       x = "Lake", y = "Number of Left Lateral Plates") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
  
  
  
  
#SL ALL BUT LINEY (bad and horrible)
ggplot (data = dataclean, aes(x = time_period, y = sl, color = body_of_water)) +
  geom_boxplot() +
  geom_line(aes(group = body_of_water), linetype=2, size=1.3) 

```


Standard Length, L plate count, R plate count, Total plate count 
```{r Plotting Numerical Unadjusted}

#SL grouped by lake
ggplot(data = dataclean, aes(x = body_of_water, y = sl, color = time_period, fill = type)) +
  geom_boxplot() +
  labs(title = "All Lakes Standard Length Historical/Present", 
       x = "Lake", y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))


#L Plate Total grouped by lake
ggplot(data = dataclean, aes(x = body_of_water, y = plate_l_total, color = time_period, fill = type)) +
  geom_boxplot() +
  labs(title = "All Lakes Total Left Lateral Plate Count Historical/Present", 
       x = "Lake", y = "Number of Left Lateral Plates") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))

```


Need to adjust so unarmoured and armoured are grouped and coloured
Body Depth, AP L and W, Jaw Length, PPL, PPW D1, D2, PS and ED
```{r Plotting Numerical Adjusted}

#Body Depth Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = body_depth.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Body Depth Historical/Present", 
       x = "Lake", y = "Body Depth Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")

#AP Length Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = ap_length.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Ascending Process Width Historical/Present", 
       x = "Lake", y = "Ascending Process Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")

#AP Width Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = ap_width.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Ascending Process Width Historical/Present", 
       x = "Lake", y = "Ascending Process Width Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")


#Jaw Length Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = jaw_length.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Jaw Length Historical/Present", 
       x = "Lake", y = "Jaw Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")


#PPL Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = ppl.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Pelvic Plate Length Historical/Present", 
       x = "Lake", y = "Pelvic Plate Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")


#PPW Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = ppw.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Pelvic Plate Width Historical/Present", 
       x = "Lake", y = "Pelvic Plate Width Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")

#D1 Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = dorsal_1.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Dorsal Spine 1 Length Historical/Present", 
       x = "Lake", y = "Dorsal Spine 1 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")

#D2 Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = dorsal_2.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Dorsal Spine 2 Length Historical/Present", 
       x = "Lake", y = "Dorsal Spine 2 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")

#PS Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = pelvic_spine.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Pelvic Spine Length Historical/Present", 
       x = "Lake", y = "Pelvic Spine Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")

#ED Adjusted grouped by Lake
ggplot(data = dataclean, aes(x = body_of_water, y = eye_diameter.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "All Lakes Eye Diameter Historical/Present", 
       x = "Lake", y = "Eye Diameter Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")


```


Parasites, AP, D1, D2, PP, PS, D3
```{r Plotting Presence/Absence}

#Parasites Boulton
ggplot(data = boulton, aes(x =  time_period, fill = parasites)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Parasites Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Parasites", values = c("orange", "seagreen4", "tomato"))

#Parasites Mayer
ggplot(data = mayer, aes(x =  time_period, fill = parasites)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Parasites Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Parasites", values = c("seagreen4", "tomato"))

#Parasites Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = parasites)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Parasites Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Parasites", values = c("seagreen4", "tomato"))

#Parasites Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = parasites)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Parasites Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Parasites", values = c("seagreen4", "tomato"))

#Parasites Rouge
ggplot(data = rouge, aes(x =  time_period, fill = parasites)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Parasites Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Parasites", values = c("orange", "seagreen4", "tomato"))



#Ascending Process Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Ascending Process Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Ascending Process Presence Mayer
ggplot(data = mayer, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Ascending Process Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Ascending Process Presence Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Ascending Process Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Ascending Process Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Ascending Process Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Ascending Process Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Ascending Process Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))




#Dorsal Spine 1 Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = dorsal_1_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Dorsal Spine 1 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Dorsal Spine 1 Presence Mayer
ggplot(data = mayer, aes(x =  time_period, fill = dorsal_1_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Dorsal Spine 1 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 1 Presence Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = dorsal_1_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Dorsal Spine 1 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 1 Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = dorsal_1_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Dorsal Spine 1 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Dorsal Spine 1 Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = dorsal_1_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Dorsal Spine 1 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred","olivedrab4"))




#Dorsal Spine 2 Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = dorsal_2_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Dorsal Spine 2 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Dorsal Spine 2 Presence Mayer
ggplot(data = mayer, aes(x =  time_period, fill = dorsal_2_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Dorsal Spine 2 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 2 Presence Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = dorsal_2_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Dorsal Spine 2 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 2 Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = dorsal_2_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Dorsal Spine 2 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 2 Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = dorsal_2_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Dorsal Spine 2 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))




#Dorsal Spine 3 Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = dorsal_3_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Dorsal Spine 3 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Dorsal Spine 3 Presence Mayer
ggplot(data = mayer, aes(x =  time_period, fill = dorsal_3_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Dorsal Spine 3 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Dorsal Spine 3 Presence Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = dorsal_3_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Dorsal Spine 3 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 3 Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = dorsal_3_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Dorsal Spine 3 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Dorsal Spine 3 Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = dorsal_3_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Dorsal Spine 3 Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))




#Pelvic Plate Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = pp_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Pelvic Plate Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))

#Pelvic Plate Presence Mayer
ggplot(data = mayer, aes(x =  time_period, fill = pp_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Pelvic Plate Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Pelvic Plate Presence Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = pp_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Pelvic Plate Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Pelvic Plate Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = pp_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Pelvic Plate Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred","olivedrab4"))

#Pelvic Plate Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = pp_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Pelvic Plate Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))




#Pelvic Spine Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = pelvic_spine_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Pelvic Spine Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))
#Pelvic Spine Presence Mayer
ggplot(data = mayer, aes(x =  time_period, fill = pelvic_spine_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Mayer Lake Pelvic Spine Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Pelvic Spine Presence Drizzle
ggplot(data = drizzle, aes(x =  time_period, fill = pelvic_spine_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Drizzle Lake Pelvic Spine Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

#Pelvic Spine Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = pelvic_spine_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Pelvic Spine Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred","olivedrab4"))

#Pelvic Spine Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = pelvic_spine_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Pelvic Spine Presence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("olivedrab4"))

```


Most common Plate arrangements (histogram by lakes past present), all four years one trait
```{r Plotting Other}

#Boulton Only showing the years all same
ggplot(data = boulton, aes(x = as.factor(year), y = body_depth.adj, color = time_period)) +
  geom_boxplot() +
  labs(title = "Boulton Lake Body Depth Historical/Present", 
       x = "Lake", y = "Body Depth Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")




#Boulton Left Historical
ggplot(data = filter(boulton, time_period == "Historical"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "purple") +
  labs(title = "Boulton Left Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#ggsave("boultonLhis.png", height = 8, width = 16, unit = "cm")
#Boulton Left Present
ggplot(data = filter(boulton, time_period == "Present"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "purple") +
  labs(title = "Boulton Left Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#ggsave("boultonLpres.png", height = 8, width = 16, unit = "cm")

#Boulton Right Historical
ggplot(data = filter(boulton, time_period == "Historical"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "purple") +
  labs(title = "Boulton Right Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Boulton Right Present
ggplot(data = filter(boulton, time_period == "Present"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "purple") +
  labs(title = "Boulton Right Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()



#Mayer Left Historical
ggplot(data = filter(mayer, time_period == "Historical"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "darkorange2") +
  labs(title = "Mayer Left Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Mayer Left Present
ggplot(data = filter(mayer, time_period == "Present"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "darkorange2") +
  labs(title = "Mayer Left Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()

#Mayer Right Historical
ggplot(data = filter(mayer, time_period == "Historical"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "darkorange2") +
  labs(title = "Mayer Right Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Mayer Right Present
ggplot(data = filter(mayer, time_period == "Present"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "darkorange2") +
  labs(title = "Mayer Right Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()



#Drizzle Left Historical
ggplot(data = filter(drizzle, time_period == "Historical"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "chartreuse4") +
  labs(title = "Drizzle Left Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Drizzle Left Present
ggplot(data = filter(drizzle, time_period == "Present"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "chartreuse4") +
  labs(title = "Drizzle Left Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()

#Drizzle Right Historical
ggplot(data = filter(drizzle, time_period == "Historical"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "chartreuse4") +
  labs(title = "Drizzle Right Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Drizzle Right Present
ggplot(data = filter(drizzle, time_period == "Present"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "chartreuse4") +
  labs(title = "Drizzle Right Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()



#Serendipity Left Historical
ggplot(data = filter(serendipity, time_period == "Historical"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "blue") +
  labs(title = "Serendipity Left Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Serendipity Left Present
ggplot(data = filter(serendipity, time_period == "Present"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "blue") +
  labs(title = "Serendipity Left Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()

#Serendipity Right Historical
ggplot(data = filter(serendipity, time_period == "Historical"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "blue") +
  labs(title = "Serendipity Right Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Serendipity Right Present
ggplot(data = filter(serendipity, time_period == "Present"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "blue") +
  labs(title = "Serendipity Right Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()



#Rouge Left Historical
ggplot(data = filter(rouge, time_period == "Historical"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "red") +
  labs(title = "Rouge Left Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#ggsave("rougeLhis.png", height = 8, width = 16, unit = "cm")
#Rouge Left Present
ggplot(data = filter(rouge, time_period == "Present"), aes(x = plate_l_combined)) +
  geom_histogram(stat = "count", fill = "red") +
  labs(title = "Rouge Left Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#ggsave("rougeLpres.png", height = 8, width = 16, unit = "cm")

#Rouge Right Historical
ggplot(data = filter(rouge, time_period == "Historical"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "red") +
  labs(title = "Rouge Right Plate Arrangements Historical", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#Rouge Right Present
ggplot(data = filter(rouge, time_period == "Present"), aes(x = plate_r_combined)) +
  geom_histogram(stat = "count", fill = "red") +
  labs(title = "Rouge Right Plate Arrangements Present", 
       x = "Plate Arrangement", y = "Count") +
  theme_minimal()
#ggsave("rougeRpres.png", height = 8, width = 16, unit = "cm")

```



Do the plots for SL, LPlate, D1, D2, and PS to merge into one big figure
```{r Multiplotting}

#SL grouped by lake
sl <- ggplot(data = dataclean, aes(x = body_of_water, y = sl, color = time_period, fill = type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))+
  scale_x_discrete(name = "", labels = c("Drizzle", "Mayer", "Serendipity", "Boulton", "Rouge"))


#L Plate Total grouped by lake
plate <- ggplot(data = dataclean, aes(x = body_of_water, y = plate_l_total, color = time_period, fill = type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(y = "Number of Left Lateral Plates") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))+
  scale_x_discrete(name = "", labels = c("Drizzle", "Mayer", "Serendipity", "Boulton", "Rouge"))


#D1 Adjusted grouped by Lake
D1 <- ggplot(data = dataclean, aes(x = body_of_water, y = dorsal_1.adj, color = time_period, fill = type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(y = "Dorsal Spine 1 Length Adjusted") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))+
  scale_x_discrete(name = "", labels = c("Drizzle", "Mayer", "Serendipity", "Boulton", "Rouge"))

#D2 Adjusted grouped by Lake
D2 <- ggplot(data = dataclean, aes(x = body_of_water, y = dorsal_2.adj, color = time_period, fill = type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(y = "Dorsal Spine 2 Length Adjusted") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))+
  scale_x_discrete(name = "", labels = c("Drizzle", "Mayer", "Serendipity", "Boulton", "Rouge"))

#PS Adjusted grouped by Lake
PS <- ggplot(data = dataclean, aes(x = body_of_water, y = pelvic_spine.adj, color = time_period, fill = type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(y = "Pelvic Spine Length Adjusted") +
  theme_minimal() +
  scale_color_manual(name = "Time Period", values = c("darkgoldenrod", "dodgerblue4"))+
  scale_fill_manual(name = "Stickleback \nType", values = c("#c7f9ff", "#d4ffeb"))+
  scale_x_discrete(name = "", labels = c("Drizzle", "Mayer", "Serendipity", "Boulton", "Rouge"))

#ggsave("SL.jpg", plot = sl, height = 10, width = 11, unit = "cm")
#ggsave("plate.jpg", plot = plate, height = 10, width = 11, unit = "cm")
#ggsave("D1.jpg", plot = D1, height = 10, width = 11, unit = "cm")
#ggsave("D2.jpg", plot = D2, height = 10, width = 11, unit = "cm")
#ggsave("PS.jpg", plot = PS, height = 10, width = 11, unit = "cm")


#ggarrange(sl, plate, D1, D2, PS, labels = c("A", "B", "C", "D", "E"))

```


```{r Plots for Export Presentation, eval=FALSE, include=FALSE}

#SL Boulton
ggplot(data = boulton, aes(x = time_period, y = sl)) +
  geom_boxplot(fill = "darkorchid1") +
  labs(title = "Boulton Lake Standard Length \nHistorical/Present", 
       x = "Time Period", y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("SLBoulton.jpg", height = 15, width = 11, unit = "cm")
#SL Drizzle
ggplot(data = drizzle, aes(x = time_period, y = sl)) +
  geom_boxplot(fill = "chartreuse3") +
  labs(title = "Drizzle Lake Standard Length \nHistorical/Present", 
       x = "Time Period", y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("SLDrizzle.jpg", height = 15, width = 11, unit = "cm")
#SL Mayer
ggplot(data = mayer, aes(x = time_period, y = sl)) +
  geom_boxplot(fill = "darkorange2") +
  labs(title = "Mayer Lake Standard Length \nHistorical/Present", 
       x = "Time Period", y = "Standard Length (mm)") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("SLMayer.jpg", height = 15, width = 11, unit = "cm")





#L Plate Mayer
ggplot(data = mayer, aes(x = time_period, y = plate_l_total)) +
  geom_boxplot(fill = "darkorange2") +
  labs(title = "Mayer Lake Total Left Lateral Plate Count \nHistorical/Present", 
       x = "Time Period", y = "Number of Left Lateral Plates") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("LPlateMayer.jpg", height = 15, width = 11, unit = "cm")
#L Plate Rouge
ggplot(data = rouge, aes(x = time_period, y = plate_l_total)) +
  geom_boxplot(fill = "firebrick2") +
  labs(title = "Rouge Lake Total Left Lateral Plate Count \nHistorical/Present", 
       x = "Time Period", y = "Number of Left Lateral Plates") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("LPlateRouge.jpg", height = 15, width = 11, unit = "cm")




#D1 Boulton
ggplot(data = boulton, aes(x = time_period, y = dorsal_1.adj)) +
  geom_boxplot(fill = "darkorchid1") +
  labs(title = "Boulton Lake Dorsal Spine 1 Length \nHistorical/Present", 
       x = "Time Period", y = "Dorsal Spine 1 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("D1Boulton.jpg", height = 15, width = 11, unit = "cm")
#D1 Mayer
ggplot(data = mayer, aes(x = time_period, y = dorsal_1.adj)) +
  geom_boxplot(fill = "darkorange2") +
  labs(title = "Mayer Lake Dorsal Spine 1 Length \nHistorical/Present", 
       x = "Time Period", y = "Dorsal Spine 1 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("D1Mayer.jpg", height = 15, width = 11, unit = "cm")
#D1 Drizzle
ggplot(data = drizzle, aes(x = time_period, y = dorsal_1.adj)) +
  geom_boxplot(fill = "chartreuse3") +
  labs(title = "Drizzle Lake Dorsal Spine 1 Length \nHistorical/Present", 
       x = "Time Period", y = "Dorsal Spine 1 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("D1Drizzle.jpg", height = 15, width = 11, unit = "cm")
#D1 Rouge
ggplot(data = rouge, aes(x = time_period, y = dorsal_1.adj)) +
  geom_boxplot(fill = "firebrick2") +
  labs(title = "Rouge Lake Dorsal Spine 1 Length \nHistorical/Present", 
       x = "Time Period", y = "Dorsal Spine 1 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("D1Rouge.jpg", height = 15, width = 11, unit = "cm")

#D2 Mayer
ggplot(data = mayer, aes(x = time_period, y = dorsal_2.adj)) +
  geom_boxplot(fill = "darkorange2") +
  labs(title = "Mayer Lake Dorsal Spine 2 Length \nHistorical/Present", 
       x = "Time Period", y = "Dorsal Spine 2 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("D2Mayer.jpg", height = 15, width = 11, unit = "cm")
#D2 Rouge
ggplot(data = rouge, aes(x = time_period, y = dorsal_2.adj)) +
  geom_boxplot(fill = "firebrick2") +
  labs(title = "Rouge Lake Dorsal Spine 2 Length \nHistorical/Present", 
       x = "Time Period", y = "Dorsal Spine 2 Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("D2Rouge.jpg", height = 15, width = 11, unit = "cm")



#PS Drizzle
ggplot(data = drizzle, aes(x = time_period, y = pelvic_spine.adj)) +
  geom_boxplot(fill = "chartreuse3") +
  labs(title = "Drizzle Lake Pelvic Spine Length \nHistorical/Present", 
       x = "Time Period", y = "Pelvic Spine Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("PSDrizzle.jpg", height = 15, width = 11, unit = "cm")
#PS Mayer
ggplot(data = mayer, aes(x = time_period, y = pelvic_spine.adj)) +
  geom_boxplot(fill = "darkorange2") +
  labs(title = "Mayer Lake Pelvic Spine Length \nHistorical/Present", 
       x = "Time Period", y = "Pelvic Spine Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("PSMayer.jpg", height = 15, width = 11, unit = "cm")
#PS Rouge
ggplot(data = rouge, aes(x = time_period, y = pelvic_spine.adj)) +
  geom_boxplot(fill = "firebrick2") +
  labs(title = "Rouge Lake Pelvic Spine Length \nHistorical/Present", 
       x = "Time Period", y = "Pelvic Spine Length Adjusted by Standard Length") +
  theme_minimal() +
  scale_color_discrete(name = "Time Period")
#ggsave("PSRouge.jpg", height = 15, width = 11, unit = "cm")


#~~~~~~~~~


#Ascending Process Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Ascending Process \nPresence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))
#ggsave("APPABoulton.jpg", height = 15, width = 11, unit = "cm")
#Ascending Process Presence Serendipity
ggplot(data = serendipity, aes(x =  time_period, fill = ap_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Serendipity Lake Ascending Process \nPresence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))
#ggsave("APPASerendipity.jpg", height = 15, width = 11, unit = "cm")



#Dorsal Spine 1 Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = dorsal_1_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Dorsal Spine 1 \nPresence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred","olivedrab4"))
#ggsave("D1PARouge.jpg", height = 15, width = 11, unit = "cm")

#Dorsal Spine 2 Presence Boulton
ggplot(data = boulton, aes(x =  time_period, fill = dorsal_2_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Boulton Lake Dorsal Spine 2 \nPresence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))
#ggsave("D2PABoulton.jpg", height = 15, width = 11, unit = "cm")
 
#Dorsal Spine 3 Presence Rouge
ggplot(data = rouge, aes(x =  time_period, fill = dorsal_3_pa)) +
  geom_bar(stat = "count", position = "fill") +
  labs(title = "Rouge Lake Dorsal Spine 3 \nPresence Historical/Present", 
       x = "Time Period", y = "Proportion of Fish") +
  theme_minimal() +
  scale_fill_manual(name = "Presence", values = c("indianred", "olivedrab4"))
#ggsave("D3PARouge.jpg", height = 15, width = 11, unit = "cm")


```


Need to figure out how to do t test for P/A
```{r Second Stats, eval=FALSE, include=FALSE}
#Oh boy this is about to be a lot of t tests
#On the adjusted values

#SL Boulton (sig increase)
t.test(sl ~ time_period, data = boulton)
#SL Drizzle
t.test(sl ~ time_period, data = drizzle)
#SL Mayer (sig increase)
t.test(sl ~ time_period, data = mayer)
#SL Serendipity
t.test(sl ~ time_period, data = serendipity)
#SL Rouge (sig decrease)
t.test(sl ~ time_period, data = rouge)


#Left Plates Boulton (Almost sig increase?)
t.test(plate_l_total ~ time_period, data = boulton)
#Left Plates Drizzle
t.test(plate_l_total ~ time_period, data = drizzle)
#Left Plates Mayer (SIG INCREASE)
t.test(plate_l_total ~ time_period, data = mayer)
#Left Plates Serendipity
t.test(plate_l_total ~ time_period, data = serendipity)
#Left Plates Rouge (SIG INCREASE)
t.test(plate_l_total ~ time_period, data = rouge)


#Right Plates Boulton (SIG increase)
t.test(plate_r_total ~ time_period, data = boulton)
#Right Plates Drizzle
t.test(plate_r_total ~ time_period, data = drizzle)
#Right Plates Mayer (SIG increase)
t.test(plate_r_total ~ time_period, data = mayer)
#Right Plates Serendipity
t.test(plate_r_total ~ time_period, data = serendipity)
#Right Plates Rouge (Huge sig increase)
t.test(plate_r_total ~ time_period, data = rouge)


#Total Plates Boulton (SIG increase)
t.test(plate_lr_total ~ time_period, data = boulton)
#Total Plates Drizzle
t.test(plate_lr_total ~ time_period, data = drizzle)
#Total Plates Mayer (SIG increase)
t.test(plate_lr_total ~ time_period, data = mayer)
#Total Plates Serendipity
t.test(plate_lr_total ~ time_period, data = serendipity)
#Total Plates Rouge  (SIG increase)
t.test(plate_lr_total ~ time_period, data = rouge)


#Body Depth Boulton (SIG increase)
t.test(body_depth.adj ~ time_period, data = boulton)
#Body Depth Drizzle (Weirdly enough sig increase)
t.test(body_depth.adj ~ time_period, data = drizzle)
#Body Depth Mayer
t.test(body_depth.adj ~ time_period, data = mayer)
#Body Depth Serendipity
t.test(body_depth.adj ~ time_period, data = serendipity)
#Body Depth Rouge (Almost sig increase)
t.test(body_depth.adj ~ time_period, data = rouge)


#AP Length Boulton
t.test(ap_length.adj ~ time_period, data = boulton)
#AP Length Drizzle
t.test(ap_length.adj ~ time_period, data = drizzle)
#AP Length Mayer
t.test(ap_length.adj ~ time_period, data = mayer)
#AP Length Serendipity (Almost sig decrease)
t.test(ap_length.adj ~ time_period, data = serendipity)
#AP Length Rouge 
t.test(ap_length.adj ~ time_period, data = rouge)


#AP Width Boulton
t.test(ap_width.adj ~ time_period, data = boulton)
#AP Width Drizzle (Almost sig decrease)
t.test(ap_width.adj ~ time_period, data = drizzle)
#AP Width Mayer
t.test(ap_width.adj ~ time_period, data = mayer)
#AP Width Serendipity (0.09 mehhhh increase)
t.test(ap_width.adj ~ time_period, data = serendipity)
#AP Width Rouge (Almost sig decrease)
t.test(ap_width.adj ~ time_period, data = rouge)


#Jaw Length Boulton
t.test(jaw_length.adj ~ time_period, data = boulton)
#Jaw Length Drizzle
t.test(jaw_length.adj ~ time_period, data = drizzle)
#Jaw Length Mayer (SIG increase)
t.test(jaw_length.adj ~ time_period, data = mayer)
#Jaw Length Serendipity (Sig decrease)
t.test(jaw_length.adj ~ time_period, data = serendipity)
#Jaw Length Rouge 
t.test(jaw_length.adj ~ time_period, data = rouge)


#Pelvic Plate Length Boulton
t.test(ppl.adj ~ time_period, data = boulton)
#Pelvic Plate Length Drizzle
t.test(ppl.adj ~ time_period, data = drizzle)
#Pelvic Plate Length Mayer
t.test(ppl.adj ~ time_period, data = mayer)
#Pelvic Plate Length Serendipity  NOPE
#t.test(ppl.adj ~ time_period, data = serendipity)
#Pelvic Plate Length Rouge 
t.test(ppl.adj ~ time_period, data = rouge)


#Pelvic Plate Width Boulton (Sig increase)
t.test(ppw.adj ~ time_period, data = boulton)
#Pelvic Plate Width Drizzle
t.test(ppw.adj ~ time_period, data = drizzle)
#Pelvic Plate Width Mayer (SIG decrease)
t.test(ppw.adj ~ time_period, data = mayer)
#Pelvic Plate Width Serendipity NOPE
#t.test(ppw.adj ~ time_period, data = serendipity)
#Pelvic Plate Width Rouge (Almost sig decrease)
t.test(ppw.adj ~ time_period, data = rouge)


#Dorsal Spine 1 Length Boulton (Sig increase)
t.test(dorsal_1.adj ~ time_period, data = boulton)
#Dorsal Spine 1 Length Drizzle (Sig increase)
t.test(dorsal_1.adj ~ time_period, data = drizzle)
#Dorsal Spine 1 Length Mayer (SIG increase)
t.test(dorsal_1.adj ~ time_period, data = mayer)
#Dorsal Spine 1 Length Serendipity
t.test(dorsal_1.adj ~ time_period, data = serendipity)
#Dorsal Spine 1 Length Rouge (SIG increase)
t.test(dorsal_1.adj ~ time_period, data = rouge)


#Dorsal Spine 2 Length Boulton (Almost sig increase)
t.test(dorsal_2.adj ~ time_period, data = boulton)
#Dorsal Spine 2 Length Drizzle (Almost sig increase)
t.test(dorsal_2.adj ~ time_period, data = drizzle)
#Dorsal Spine 2 Length Mayer (Sig increase)
t.test(dorsal_2.adj ~ time_period, data = mayer)
#Dorsal Spine 2 Length Serendipity
t.test(dorsal_2.adj ~ time_period, data = serendipity)
#Dorsal Spine 2 Length Rouge (Sig increase)
t.test(dorsal_2.adj ~ time_period, data = rouge)


#Pelvic Spine Length Boulton
t.test(pelvic_spine.adj ~ time_period, data = boulton)
#Pelvic Spine Length Drizzle (Sig increase)
t.test(pelvic_spine.adj ~ time_period, data = drizzle)
#Pelvic Spine Length Mayer (SIG increase)
t.test(pelvic_spine.adj ~ time_period, data = mayer)
#Pelvic Spine Length Serendipity NOPE
t.test(pelvic_spine.adj ~ time_period, data = serendipity)
#Pelvic Spine Length Rouge (SIG increase)
t.test(pelvic_spine.adj ~ time_period, data = rouge)


#Eye Diameter Boulton (Sig decrease)
t.test(eye_diameter.adj ~ time_period, data = boulton)
#Eye Diameter Drizzle
t.test(eye_diameter.adj ~ time_period, data = drizzle)
#Eye Diameter Mayer (Sig decrease)
t.test(eye_diameter.adj ~ time_period, data = mayer)
#Eye Diameter Serendipity (Sig increase)
t.test(eye_diameter.adj ~ time_period, data = serendipity)
#Eye Diameter Rouge WHOOPS
#t.test(eye_diameter.adj ~ time_period, data = rouge)



#Still need to do T test for P/A of Parasites, AP, D1, D2, PP, PS, D3
```

